### 2022-01-03 doc/contrastive-learning.tex
adds some pictures for clustering
adds table with first set of pretraining results

@@

>>>>

Honestly still confused by some of these methods.

\begin{figure}[h!]
    \begin{center}
        \includegraphics[scale=0.35]{images/swav.png}
        \caption{Visualization of SwAV \cite{caron_unsupervised_2021}}
    \end{center}
\end{figure}

\begin{figure}[h!]
    \begin{center}
        \includegraphics[scale=0.35]{images/prototypes.png}
        \caption{Visualization of PCL training framework \cite{li_prototypical_2021}}
    \end{center}
\end{figure}

\begin{figure}[h!]
    \begin{center}
        \includegraphics[scale=0.35]{images/byol.png}
        \caption{Visualization of BYOL \cite{grill_bootstrap_nodate}}
    \end{center}
\end{figure}

@@

\section{Results}

\subsection{Experimental Setup}

hyper-parameters:

batch size: 16
accumulate gradient: 3
learning rate: 0.2
iterations: 4000

\subsection{Semantic Segmentation Negative Sampling}

\begin{center}
    \begin{table}[h!]
        \resizebox{\textwidth}{!}{
            \begin{tabular}{ c | c c c c c c c c c c c c c | c }
                              & ceiling        & floor          & wall           & beam           & column         & window         & door           & table          & chair          & sofa           & bookcase       & board          & clutter        & mIOU           \\
                \hline
                baseline      & 0.869          & 0.95           & 0.798          & \textbf{0.001} & 0.253          & \textbf{0.585} & 0.510          & 0.731          & \textbf{0.841} & 0.391          & 0.715          & \textbf{0.725} & 0.534          & 0.608          \\
                PointContrast & \textbf{0.895} & \textbf{0.961} & \textbf{0.817} & 0              & \textbf{0.350} & 0.561          & \textbf{0.671} & \textbf{0.737} & 0.834          & \textbf{0.572} & \textbf{0.727} & 0.699          & \textbf{0.554} & \textbf{0.644}
            \end{tabular}
        }
        \caption{S3DIS pretraining results on Semantic Segmentation}
    \end{table}
\end{center}
